Light inextensible strings under tension in the Schwarzschild geometry

### 2018-10-01 string_microarticle.tex
sharpen up the wording

\section{Results}
Solutions to equation~\ref{rdashdash} fall into two distinct classes:
those with two free ends, and those with one free end (the other
``end'' is tangential to the event horizon, in general).

Figure~\ref{closest_approach_non_self_intersecting} shows non-self
intersecting strings indexed by minimum distance of approach to the
singularity, which is taken to occur at~$\phi=0$.  Strings with a
sufficiently close passage to the event horizon self-intersect
(Figure~\ref{closest_approach_self_intersecting}).  Numerical methods
show that the critical value is~$\simeq 1.076109317$, with an
uncertainty of~1 in the last digit: if the closest approach is less
than this value, the string crosses itself at~$\phi=\pi/2$.
Figure~\ref{fixed_EH_intersection} shows some strings that are tangent
to the event horizon at~$\phi=0$.

@@

In Figure~\ref{closest_approach_non_self_intersecting}, one's
classical intuition would suggest that the black hole feels a force to
the left, and should start accelerating.  However, it is not clear by
what mechanism such a force would be transmitted: the situation is
steady, so no gravitational waves are produced; the string is
inextensible, so stores no energy.  Likewise,
Figure~\ref{fixed_EH_intersection} would suggest that angular momentum is
transmitted to the black hole, but no mechanism is apparent.

This work considered only the Schwarzschild metric and generalizing it
to the Kerr metric~\cite{kerr1963} might be interesting.

>>>>

\section{Results}
Solutions to equation~\ref{rdashdash} fall into two distinct classes:
those with $r>1$ at all points, and those which attain $r=1$, in which
case the string is tangential to the event horizon, in general.
Considering first cases with $r>1$, numerical methods show that if the
closest approach is greater than a critical value of~$\simeq
1.076109317(1)$, the string does not self-intersect
(Figure~\ref{closest_approach_non_self_intersecting}); if the closest
approach is less than this value, the then string crosses itself
at~$\phi=\pi/2$ (Figure~\ref{closest_approach_self_intersecting}).
The case where the string is tangent to the event horizon
at~$r=1,\phi=0$ is shown in Figure~\ref{fixed_EH_intersection}.

@@

In Figure~\ref{closest_approach_non_self_intersecting}, one's
classical intuition would suggest that the black hole feels a force to
the left, and should start accelerating.  However, it is not clear by
what mechanism such a force would be transmitted: the situation is
steady, so no gravitational waves are produced; the string is
inextensible, so stores no energy.  This work considered only the
Schwarzschild metric and generalizing it to the Kerr
metric~\cite{kerr1963} might be interesting.
